Precision calculations of the cosmic shear power spectrum projection

### 2017-03-09 limber2.tex
Updated figures with Ludo's wigner-d calculations (however; more updates need to be done using the corrected calculations); added comment on missing (now correct) a^2 in the Van de Rijt derivation

Inserting equation~(\ref{eqn:B1}) into the second-order Limber power spectrum
in equation~(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson
equation to replace the matter with the potential power spectrum we obtain the
same expression as \cite{vande2012} (their Equation~7.19), except for an
additional factor $a^2(\chi)$. This difference is accounted for by the factor
$a^{-1}$ in the propagation of primordial potential perturbations to late
times, see Equation~(6.22) in \cite{vande2012}, where the transition is
calculated using $g(a)$ instead of $D(a)$.

@@

\cite{2012MNRAS.422.2854G} derive the flat-sky lensing power spectrum in their
Equations (25) and (26). Their window function $W^{\varepsilon_i}$ defined in
their Equation (25) for a flat Universe equals $\pref q(\chi) / a(\chi)$, since
${\rm d} z \, ({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to
a typo there is a factor $r_K[r(z)]$ missing in the window function, which
translates into a missing $r_K[r] r_K[r^\prime]$ in the full projection
integral\footnote{Typo confirmed by T.~G., priv.~comm.}. This also leads to an
errorous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
accounted for, and making the additional approximation $k \chi \approx k
\chi^\prime \approx \ell$ (see their Appendix~\ref{sec:schmidt08}) we reproduce
the expressions of \cite{2012MNRAS.422.2854G}.

>>>>

Inserting equation~(\ref{eqn:B1}) into the second-order Limber power spectrum
in equation~(\ref{eq:C_ell_limber2_dr_s}) and using the inverse Poisson
equation to replace the matter with the potential power spectrum we obtain the
same expression as \cite{vande2012} (their Equation~7.19).

\EDIT{Note: The factor of $a^2$ has been resolved, it is correctly reproduced
when propagating the primordial potential power spectrum to late times $a$
with $[D+(a)/a]^2$ instead of $D^2+(a)$.}

%, except for an
%%additional factor $a^2(\chi)$. This difference is accounted for by the factor
%$a^{-1}$ in the propagation of primordial potential perturbations to late
%times, see Equation~(6.22) in \cite{vande2012}, where the transition is
%calculated using $g(a)$ instead of $D(a)$.

@@

\cite{2012MNRAS.422.2854G} derive the flat-sky lensing power spectrum in their
Equations (25) and (26). Their window function $W^{\varepsilon_i}$ defined in
their Equation (25) for a flat Universe equals $\pref q(\chi) / a(\chi)$, since
${\rm d} z \, ({\rm d} N(z)/{\rm d} z) = {\rm d} \chi n(\chi)$; however due to
a typo there is a factor $r_K[r(z)]$ missing in the window function, which
translates into a missing $r_K[r] r_K[r^\prime]$ in the full projection
integral\footnote{Typo confirmed by T.~G., priv.~comm.}. This also leads to an
errornous $r_K^{-2}(r)$ in their Limber equation (27). With these factors
accounted for, and making the additional approximation $k \chi \approx k
\chi^\prime \approx \ell$ (see their Appendix~\ref{sec:schmidt08}) we reproduce
the expressions of \cite{2012MNRAS.422.2854G}.
